\begin{enumerate}[(i)]
	\item We assume \textsc{Alg}$(G, \varepsilon)$ is an FPTAS that computes a $(1 - \varepsilon)$-approximation for \textsc{MaximumIndependentSet} on a graph $G$.
		We want to use this algorithm to compute an exact answer, which means that the error $\varepsilon$ should be so small that $(1 - \varepsilon) \text{OPT} > \text{OPT} - 1$, better than the optimal solution - 1.

		\begin{equation}
		\begin{split}
			(1 - \varepsilon) \text{OPT} &> \text{OPT} - 1\\
			\text{OPT} - \varepsilon \text{OPT} &> \text{OPT} - 1\\
			- \varepsilon \text{OPT}& > -1\\
			\varepsilon \text{OPT} &< 1\\
		\end{split}
		\end{equation}

		We know that $|V|$ is an upper bound for OPT.
		$1 \leq OPT \leq |V|$.

		It follows that if we pick $\frac{1}{|V|+1}$ for $\varepsilon$, our FPTAS will always give the optimal solution.
		Thus, the algorithm is as follows:

\begin{sourcecode}
\algorithm{ExactMaximumIndependentSetPolynomial($G=(V,E)$)}
\return \textsc{Alg}$(G, \frac{1}{|V| + 1})$
\qend
\end{sourcecode}

		We derived an exact algorithm for \textsc{Maximum Independent Set} that runs in polynomial time using an (any, unspecified) FPTAS.
		\textsc{MaximumIndependentSet} is NP-hard, so there cannot exist an exact algorithm that runs in polynomial time.
		Since the existence of an FPTAS for this problem leads to an exact solution that runs in polynomial time, such an FTPAS can not exist (unless P=NP).

	\item No, the proof in (i) only implies that there is no FPTAS for \textsc{Maximum Independent Set} unless P=NP.

		We only reach a contradiction in the proof in (i) because the running time is polynomial.
		However, in a PTAS, the running time could be non-polynomial, for instance if $\varepsilon$ is in a power.

		Thus, there could still be a general PTAS, in which $\varepsilon$ is not polynomial.
\end{enumerate}
