\begin{enumerate}[(i)]
	\item In the best case, the same literal shows up in all clauses.
		Thus, we have
		\[
		OPT \geq 1
		\]
		as the lower bound.

		Consider the following CNF with $m$ clauses
		\[
			(x_1 \lor x_2 \lor x_3) \land (x_4 \lor x_5 \lor x_3) \land (x_6 \lor x_7 \lor x_3) \land \ldots \land (x_{2m} \lor x_{2m+1} \lor x_3)
		\]

		Then, the algorithm could pick the $x_1, x_4, x_6, \ldots, x_{2m}$, $m$ literals.
		Note that we have $2m + 1$ variables, so $n = 2m + 1$.
		This is the worst case possible because since no literals can be negated, picking one literal from each clause and setting it to true will always result in true.

		Take $T$ to be the number of literals set to true by the algorithm.
		Then,
		\begin{equation}
		\begin{split}
			T & \leq m  \\
				& \leq \frac{n-1}{2}\\
				& \leq \frac{n-1}{2} * LB \\
				& \leq \frac{n-1}{2} * OPT
		\end{split}
		\end{equation}

		So, the given algorithm is a $\frac{n-1}{2}$-approximation.
	\item The algorithm below uses the same priciples as \textsc{Approx-Vertex-Cover} which was treated in the lecture.
        It assumes the CNF formula is represented as $F=(V,C)$, where $V$ is the set of variables and $C$ is the set of clauses in the formula.

\begin{sourcecode}
\algorithm{Approx-3-CNF($F=(V,C)$)}
\comment{$T$ is the set of variables to set to true}
$T = \emptyset$
\comment{$C^*$ is the set of clauses that does not contain one or more variables that are in $T$}
$C^* = C$
\while{$C^* \neq \emptyset$}
	Take a clause $(a, b, c)$ in $C*$
	$T = T \cup \{a, b, c\}$
	Remove all clauses that contain one or more of $a$, $b$ or $c$ from $C^*$
|
\return{$T$}
\qend
\end{sourcecode}

		Two clauses are non-overlapping if they don't have any variables in common.\\%Yeah yeah, I know.
		\\
		Let $N \subseteq C$ be any set of non-overlapping edges. Then OPT $\geq N$.\\
		\\
		Consider any input formula $F$.

		Let $N$ be the set of clauses selected in step 6 of the algorithm.

		$N$ is a set of non-overlapping clauses, so OPT($F$) $\geq |N|$.

		$|T| = 3|N|$.

		Hence, $\textnormal{ALG}(F) = |T| = 3|N| \leq 3 \textnormal{OPT}(F)$.\\
		\\
		So \textsc{Approx-3-CNF} is a 3-approximation for 3-CNF.
\end{enumerate}
